---
title: "Lab 1 Questions"
author: "Omima Hassan"
date: "9/5/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Understanding Concepts 

  1. Explain the difference between Git and Github.
  
   + Git is a version control system that helps developers track their changes in code while making it easier to peer      develop while Github is a hosting service that allows Git projects to be presented online.
  
  2. Can Git and Github be used independently? Why don't we do so? Describe the advantages and disadvantages. 
  
   + Yes Git and Github can be used independently but we dont do it because it makes it difficult to work in a team. An advantage of using the two together is that it allows for a    connection when  peer coding, it makes it easier to work on a project with others because each teammate can see all the changes made and collaborate on their own as well. A disadvantage to not using the two is making it difficult to collaborate because changes aren't shown and may be repeated. 

  3. What is a repository in Git and how can you create a repository in Git (write out the command(s))? 
   
   + A repository is a folder for a project in Github, to create a repository you would write these commands in Git Bash
   + 1. Create a new repository in GitHub
   + 2. Clone your GitHub url using $ git clone https://github.com/whateverusername/filename.git
   + 3. Open up GIt Bash and initialize the local directory using $git init
   + 4. Add the files that you would like to be in the repository using $git add
   + 5. Commit the files using $ git commit -m "Made initial changes"
   + 6. Push your changes using $git push -u origin master
   + 7. To check if your new files were updated use $git pull and it will let you know if the files are up to date or not
   + 8. Using $git status also lets you know whats going on with your file as well
   
# Coding Exercises 

1. Write code to count the total number of `NA` occurrences in the vector `X = c(47,34,33,65,37,NA,43,NA,11,NA,23,NA)`.
``` {r}
X = c(47,34,33,65,37,NA,43,NA,11,NA,23,NA)
sum(is.na(X))

```

2. Run the following code and change 0 value to 150
``` {r}
age = c(25,30,45,60,12,41)
   smoker = c('T','F','T','F','F','F')
   weight = c(120,137,0,168,91,142)
   example_data = data.frame(age,smoker,weight)
   replace(weight, weight ==0, 150)
 
```

3. Turn code snippets into functions
``` {r}
#Finds the mean of all NA values

mean_na = function(x)
{
   mean(is.na(x))
}

```


```{r}
#Takes a vector and sums it to 1

sum_vec = function(x)
{
   x / sum(x, na.rm = TRUE)
}

```

4. Write a function named both_na(). This function take two vectors of the same length and returns the number of positions that have an NA value in both vectors.
```{r}
both_na = function(x,y)
{
   sum(is.na(x) & is.na(y))
}
 x= c(NA, NA, 1, 2, NA, NA, 1)
 y= c(NA, NA, 1, 2, NA, NA, 1)
 both_na(x,y)
```
