---
title: "Lab 1"
author: "Omima"
date: "9/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Collaborating on a Repository

 1. Name
  
   + Omima Hassan
   
 2. What do you tell people about your field of study at a party?
  
   + Involves a lot of programming
   
 3. What are the three most important tools/ strategies you use for organizing your work?
 
   + Writing it down on a calendar
   + Sticky notes
   + To- do lists
   
 4. Interesting fact about yourself?
   + I'm bilingual 




# Understanding Concepts 

  1. Explain the difference between Git and Github.
  
   + Git is a version control system that helps developers track their changes in code while making it easier to peer      develop while Github is a hosting service that allows Git projects to be presented online.
  
  2. Can Git and Github be used independently? Why don't we do so? Describe the advantages and disadvantages. 
  
   + Yes Git and Github can be used independently but we dont do it because it makes it difficult to work in a team. An advantage of using the two together is that it allows for a    connection when  peer coding, it makes it easier to work on a project with others because each teammate can see all the changes made and collaborate on their own as well. A disadvantage to not using the two is making it difficult to collaborate because changes aren't shown and may be repeated. 

  3. What is a repository in Git and how can you create a repository in Git (write out the command(s))? 
   
   + A repository is a folder for a project in Github, to create a repository you would write these commands in Git Bash
   + 
   
# Coding Exercises 

1. Write code to count the total number of `NA` occurrences in the vector `X = c(47,34,33,65,37,NA,43,NA,11,NA,23,NA)`.

``` {r}
X = c(47,34,33,65,37,NA,43,NA,11,NA,23,NA)
sum(is.na(X))

```
2. Run the following code and change 0 value to 150
``` {r}
age = c(25,30,45,60,12,41)
   smoker = c('T','F','T','F','F','F')
   weight = c(120,137,0,168,91,142)
   example_data = data.frame(age,smoker,weight)
   replace(weight, weight ==0, 150)
 
```
3. Turn code snippets into functions
``` {r}
x = c(5,8,9)
mean(is.na(x))
x/ sum(x, na.rm = TRUE)
```

4. Write a function named both_na(). This function take two vectors of the same length and returns the number of positions that have an NA value in both vectors.
```{r}

```